A Decision Procedure for (Co)datatypes in SMT Solvers

### 2016-02-09 sister/sister.tex
tune

\newcommand\captioni{\,Number of solved goals with 16~lemmas per goal}
\newcommand\captionii{\,Number of solved goals with 256~lemmas per goal}

@@

\begin{table}[t!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}c@{\kern.5em}c@{\kern1em}c@{\kern.5em}c@{\;}}
  & \multicolumn{2}{@{}c@{\kern1em}}{16 lemmas\;} & \multicolumn{2}{@{}c@{\;}}{256 lemmas} \\%[-0.5pt]
  & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{\,Z3}
\MIDRULE
No (co)datatypes
 &  1099  &  1097  &  2209  &  1911 \\%[\jot]
Datatypes without \rn{Acyclic}
 &  1116  &  -- &  2211  &  -- \\
Full datatypes
 &  1120  &  1121  &  2211  &  1901 \\%[\jot]
Codatatypes without \rn{Unique}\!\!
 &  1132  &  --  &  2208  &  -- \\
Full codatatypes
 &  1137  &  -- &  \bfseries 2220  &  -- \\%[\jot]
Full (co)datatypes
 &  \bfseries 1157  &  -- &  2219  &  -- %\\[\jot]
\end{tabular}\end{center}
\caption{\captioni}
\label{tab:bench}
\end{table}

>>>>

\newcommand\captioni{\,Number of solved goals with $n$~lemmas per goal}
\newcommand\captionii{\,Number of solved goals with 256~lemmas per goal}

@@

\begin{table}[t!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}c@{\kern.5em}c@{\kern1em}c@{\kern.5em}c@{\;}}
  & \multicolumn{2}{@{}c@{\kern1em}}{$n = 16$\,} & \multicolumn{2}{@{}c@{\;}}{$n = 256$\;} \\%[-0.5pt]
  & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{\,Z3}
\MIDRULE
No (co)datatypes
 &  1099  &  1097  &  2209  &  1911 \\%[\jot]
Datatypes without \rn{Acyclic}
 &  1116  &  -- &  2211  &  -- \\
Full datatypes
 &  1120  &  1121  &  2211  &  1901 \\%[\jot]
Codatatypes without \rn{Unique}\!\!
 &  1132  &  --  &  2208  &  -- \\
Full codatatypes
 &  1137  &  -- &  \bfseries 2220  &  -- \\%[\jot]
Full (co)datatypes
 &  \bfseries 1157  &  -- &  2219  &  -- %\\[\jot]
\end{tabular}\end{center}
\caption{\captioni}
\label{tab:bench}
\end{table}
